---
title: "A Searchable Database of Allegheny County Election Division's Potentially Incorrect Ballots"
date: '2022-11-07'
output: 
  html_document:
    toc: true
    toc_float: true
    code_download: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(httr)
library(DT)
library(readxl)
library(kableExtra)

# Load data in steps xlsx files

# URL to object "url1" - "No Date"
url1 <- "https://www.alleghenycounty.us/uploadedFiles/Allegheny_Home/Dept-Content/Elections/Docs/No%20Date.xlsx"

# Use httr to write the object to a temp file on disk
GET(url1, write_disk(tf1 <- tempfile(fileext = ".xlsx")))

# Read the file using readxl package, attach the name given by the PHL
# City Commissioners to this file as a column
df1 <- read_excel(tf1, skip = 2) %>%
  mutate(Issue = "No Date")

# Repeat for file 2 - Incorrectly Dated
url2 <- "https://www.alleghenycounty.us/uploadedFiles/Allegheny_Home/Dept-Content/Elections/Docs/Incorrectly%20Dated.xlsx"

GET(url2, write_disk(tf2 <- tempfile(fileext = ".xlsx")))

df2 <- read_excel(tf2, skip = 2) %>%
  mutate(Issue = "Incorrectly Dated")

# Bind the data sets together
dat <- rbind(df1, df2)

# Filter out rows that are entirely NA

dat <- dat %>%
  filter(is.na('Last Name') == FALSE &
                is.na('First Name') == FALSE &
           is.na(Municipality) == FALSE &
           is.na(Precinct) == FALSE)

```

# What is this document?

You can use this site to to see if your 2022 mail-in ballot for the November election was listed as "potentially incorrect" by the Allegheny County Elections Division (as of Nov. 6th) and in need of correction.

For information about how to correct your ballot, [please visit the Election Division's website](https://www.alleghenycounty.us/elections/incorrect,-no-date-ballots.aspx).

On November 6th, 2022, the Allegheny County Elections Division publicly published lists of ballots that might be "potentially incorrect" for various reasons. [They published 2 pdf and 2 Excel files to their website](https://www.alleghenycounty.us/elections/incorrect,-no-date-ballots.aspx) with lists of mail-in-ballots that had potential problems. The [announcement read](https://www.alleghenycounty.us/elections/incorrect,-no-date-ballots.aspx):

*"As there is not opportunity to notify impacted voters by letter of this decision and their opportunity to cure, we are instead providing a list of those voters who returned ballots in these two categories: no date and incorrectly dated."*

*"Voters may come to the Elections Division office, 326 County Office Building (3rd floor), 542 Forbes Avenue in downtown Pittsburgh and present photo ID and will be provided the opportunity to cure. This opportunity is available during regular business hours of 8:30 AM to 4:30 PM on Monday, November 7, 2022 and from 7 AM to 8 PM on Election Day, Tuesday, November 8, 2022."*

The Elections Division site also provides options for people who cannot travel due to disability and options for provisional ballots.

The databases they published were not searchable in a web browser. This site formats the data in a searchable tool.

This tool points directly to the URLs published by the Elections Division. The code used to generate this searchable database [is open source and available](https://github.com/mafichman/incorrectBallotsPGH).
This site is not associated with the Allegheny County Elections Division, any government, political party, political action committee, or any election entity.

# Search for your ballot

Search the database below to see if your ballot was flagged as "potentially incorrect."

```{r datatable, echo=FALSE}
datatable(dat, 
          options = list(pageLength = 10))
```
**Attribution and Sourcing**

This tool was created by Michael Fichman on 11/7/2022 using data published by the the Elections Division on 11/6/2022. The code is available [on Github](https://github.com/mafichman/incorrectBallotsPGH).

There is an equivalent tool for Philadelphia County that can be found [here](https://mafichman.github.io/PotentiallyIncorrectBallots/).